---
title: "project_Xu"
author: "Jiehan Xu"
date: "5/3/2020"
output: html_document
---
First initialize needed packages. The document api-keys.r keeps all the api keys I used for the project.
```{r}
library(tidyverse)
library(lubridate)
library(stringr)
library(ggplot2)
library(gutenbergr)
library(tidytext)
library(rvest)
library(httr)
library(curl)
library(jsonlite)
library(dplyr)
library(pool)
library(modelr)
library(purrr)
library(broom)
library(tidyr)
library(wordcloud)
source("/Users/jane/Downloads/data\ wrangling/project/api-keys.R")
```
1.IMDb Ranking Scrapping
First of all, I scrap the top 250 rating movies table from IMDB site. The initial table I get only has two variables: one is rank, title, year of the movies, another is the rating. I tidy the data frame (delete the "()" and blank space and tranfer year and rating into numeric variables) and separate it into four variables: film title, year, imdb_rating, and the rank of rating. 

```{r}
##----script the rank on IMDb site----
rank <- "https://www.imdb.com/chart/top/?ref_=nv_mv_250" %>%
  read_html() %>% 
  html_table(fill = TRUE)%>%.[[1]]
names(rank)[names(rank)=="Rank & Title"] <- "film_title"
names(rank)[names(rank)=="IMDb Rating"] <- "imdb_rating"
rank <- rank[,2:3]
#tidy the data frame and keep title, year, rating and rank of IMDb
tidy_rank <-rank %>% 
  separate(film_title,c("rank","film_title","year"),sep="\n") %>%
  select(film_title,year,imdb_rating) %>%
  mutate(n_rank=min_rank(desc(imdb_rating)))
tidy_rank$year <- tidy_rank$year %>%
  str_replace_all("        ","") %>%
  str_replace_all("\\(","") %>%
  str_replace_all("\\)","") %>%
  as.numeric()
tidy_rank$film_title <- tidy_rank$film_title %>%
  str_replace_all("      ","")
head(tidy_rank)
tidy_rank %>%
  group_by(year) %>%
  summarise(total=n()) %>%
  arrange(desc(total))
```
Arrange the data frame and I get the top 6 movies shown in the results, among them only 4 have a rating above 9.0 point: The Shawshank Redemption, with a rating of 9.2; The Godfather,with a rating of 9.1; The Godfather: Part II, with a rating of 9.0; The Dark Knight, with a rating of 9.0.
I also used summerise function to count numer of top 250 movies each year and find out that year 1995 has the largest number 8. 

2. OMDb API combine with IMDb ranking
Because the IMDb ranking website only lists limited information about each movie, in order to digging out further information, I also used OMDb API to get information such as box office, director, runtime and actors.

After reading the instruction on OMDb API site, I choose to obtain movie information by seaching the title of the movies. I use a loop to combine the information of 250 movies together. 

```{r}
omdb_title <- tidy_rank$film_title %>%
  str_replace_all("Taare Zameen Par","Like Stars on Earth")%>%
  str_replace_all("Capharnaüm","Capernaum")%>%
  str_replace_all("Rashômon","Rashomon")%>%
  str_replace_all("Babam ve Oglum","My Father and My Son")%>%
  str_replace_all("Relatos salvajes","Wild Tales")%>%
  str_replace_all("Kis Uykusu","Winter Sleep")%>%
  str_replace_all(" ","+")
```
Because the film title I get on IMDb Ranking sites are the original names and some of them do not match the name in OMDB database. Error occurs several times when running the progrmam. After manually changing the names of several films using str_replace_all function, I finally get the specific information of the 250 films.
```{r}
omdb_result <- 0
for (i in 1:length(omdb_title)){
  url <- paste0(
    "http://www.omdbapi.com/?apikey=", 
    api.key.Xu.omdb,"&t=",omdb_title[i],"&y=&plot=short&r=json?")
  omdb_each <- url %>% curl() %>% readLines() %>%
    prettify() %>%
    fromJSON() %>%as.data.frame()
  omdb_result <- rbind(omdb_result,omdb_each)
}
omdb_imdb <- omdb_result %>%
  filter(Ratings.Source=="Internet Movie Database")
```
The data frame I get has 26 variables, and 704 obs. From variable Ratings.Sources, I find that OMDb lists three ratings souces of movies: Internet Movie Database (IMDb), Rotten Tomatoes, Metacritic. Because some movies do not have a Rotten Tomatoes or Metacritic ratings, I filter out these two ratings sources and only keep observation with IMDB ratings. So the new data frame has 26 variables, and 250 obs.

(1) Company
By counting and ranking the number of films each company produced according to the variable “Production”, I plot the bar plot below:
```{r}
#Which production company is popular
omdb_imdb %>%
  group_by(Production) %>%
  summarise(total=n()) %>%
  filter(total>5)%>%
  mutate(Production = reorder(Production, total))%>%
  ggplot(aes(Production, total)) + 
  geom_bar(stat = "identity") +
  xlab(NULL) + coord_flip() +
  ggtitle("common production in IMDb top 250 rating")
##average rating of company
omdb_imdb$Ratings.Value <-omdb_imdb$Ratings.Value %>%
  str_replace_all("\\/10","") %>%
  as.numeric()
omdb_imdb %>%
  group_by(Production) %>%
  summarise(mean=mean(Ratings.Value)) %>%
  arrange(desc(mean))
```
Apart from films with a N/A value of production company, Warner Bros. Pictures produces largest number of movies among top 250 rating. And if I treat Warner Bros. Picture and Warner Bros. as the same company, the superiority of Warner Bros. for producing high rating films is obvious.

(2)Genre
Moreover, I am interested in finding out which genre may be more likely to get a higher rating. To answer this question, I use variable “Genre”. Simply using “group_by” and “summarise” functions is not wise, because a film can belong to several genre. Take film “Spirited Away” as an example, the value of its variable “Genre” is “Animation, Adventure, Family, Fantasy, Mystery”. 

In order to fairly count the appearance of genres of the 250 movies, I separate one movie into several observations, each observation only contains one genre. I use “separate” and “gather” functions to achieve it. After filtering NA values, I expand the original 250 observations to 708 observations. 
```{r}
#Which genre is popular
tidy_genre<- omdb_imdb %>%
  separate(Genre,into=c("1","2","3","4","5","6"),sep=", ") %>%
  gather("1":"6",key=n_genre,value=genre)%>%
  na.omit(genre)
##average ratins points of genre
tidy_genre %>%
  group_by(genre) %>%
  summarise(total=n()) %>%
  arrange(desc(total))
tidy_genre %>%
  group_by(genre) %>%
  summarise(mean=mean(Ratings.Value)) %>%
  arrange(mean)
tidy_genre %>% 
  group_by(genre) %>%
  summarise(total=n()) %>%
  mutate(genre = reorder(genre, total))%>%
  ggplot(aes(genre, total)) + 
  geom_bar(stat = "identity") +
  xlab(NULL) + coord_flip() +
  ggtitle("most common genre in IMDb top 250 Rating")
```
“Drama” is the most common genre among the top 250 rating movies, as it shows up in 184 movies. “Thriller”, “Adventure”, “Crime” are also popular genres, which show up 61, 57, 52 times respectively. I also calculate the average ratings of movies under each genre and get the results that genre “Action” and “Horror” have the highest average rating value, 8.35; genre “Sport” has the lowest average rating value, 8.17.

(3)Country
Similar with the discussion of genre, the variable “Country” can also contain several countries in an observation. Repeating the steps of finding most common genre, I also get the country distribution picture.

From bar plot below I find that, the U.S. is far ahead other countries and among the top 250 movies, 170 movies are from the U.S. This is reasonable because American films also take a large proportion in global film market. Furthermore, American takes a large proportion of IMDb voters, which makes American movies more likely to be rated.
```{r}
#which country is popular
tidy_country<- omdb_imdb %>%
  separate(Country,into=c("1","2","3","4","5","6"),sep=", ") %>%
  gather("1":"6",key=n_country,value=country)%>%
  na.omit(country)
tidy_country %>%
  group_by(country) %>%
  summarise(total=n()) %>%
  arrange(desc(total))
tidy_country %>% 
  group_by(country) %>%
  summarise(total=n()) %>%
  mutate(country = reorder(country, total))%>%
  ggplot(aes(country, total)) + 
  geom_bar(stat = "identity") +
  xlab(NULL) + coord_flip() +
  ggtitle("most common country in IMDb top 250 Rating")
```

(4) Actors
Similar with the discussion above, this time I choose to discuss variable “Actors”. The database only shows 4 main actors/actresses for each movie and save the rest as factors. Repeating the steps in (2) and (3) and I get the plot of popular actors/actresses.

Mr. Robert De Niro, who is famous for acting in The Godfather Part II and received numerous accolades, takes the top without suspense. 
```{r}
#famous actor/actress
tidy_act<- omdb_imdb %>%
  separate(Actors,into=c("1","2","3","4","5","6"),sep=", ") %>%
  gather("1":"4",key=n_actor,value=actor)
tidy_act %>% 
  group_by(actor) %>%
  summarise(total=n()) %>%
  mutate(actor = reorder(actor, total))%>%
  filter(total>3)%>%
  ggplot(aes(actor, total)) + 
  geom_bar(stat = "identity") +
  xlab(NULL) + coord_flip() +
  ggtitle("most common actor/actress in IMDb top 250 Rating")
```

(5) Runtime and Rating Value
After doing some research on country, genre and company of the movies, I change my angle of view to the relationships between variables. The first comes into my mind is the relationships between runtime and the rating value. I tidy the variable “Runtime” and make it numeric, then draw the boxplot of rating value and runtime.

From box plot I find that, generally, the runtime of most of the 250 movies is below 200 minutes. Because there is only one film under circumstances rating value is 9.3 or 9.2, I choose to ignore these two observations and only discuss movies with a rating between 8.0 and 9.0. 

Movies with a longer runtime seem more likely to get a higher rating value when the rating value is between 8.5 and 9.0. And there is not obvious pattern between runtime and rating value for movies rating under 8.5. Moreover, movies with a lower rating value are more various in runtime, especially for rating value 8.2, the difference between maximum and minimum runtime is huge. 
```{r}
#relation between rating value and runtime
tidy_relation <- omdb_imdb %>%
  select(Title, Year, Runtime, imdbRating, BoxOffice)
tidy_relation$Runtime <- tidy_relation$Runtime %>%
  str_replace_all(" min","")%>%
  as.numeric()

tidy_relation %>%
  ggplot(aes(imdbRating,Runtime)) + 
  geom_boxplot()+
  theme(axis.text.x = element_text(size = 5,angle = 90))+
  ggtitle("boxplot between rating and runtime")
```

(6) Box Office and Rating Value
Similarly, I discuss the relationships between rating value and boxoffice using boxplot. Before plotting the graph, I apply regular expression to tidy the variable “BoxOffice” and make it numeric. 

When the rating value is above 8.3 and only looking at the medium value of each rating value, I find that movies with a higher rating value typically has a larger box office. The movies with a lower rating values may have a larger uncertainty of box office, as outliers start to appear when the rating value is below 8.5. A good example is the movie “Avengers: Infinity War”. This movie gets the highest box office among the 250 movies, excess the second highest “The Dark Knight” (rating value is 9.0) and its rating value is 8.5.

Apart from boxplot, I also simply list the top 6 highest box office and top 6 lowest box office movies. I find that movies with lower box office are more likely to be movies before 1990, while movies with higher box office are closer to present, which means the box office also related to the year of release.
```{r}
#relation between rating and boxoffice
tidy_relation <- tidy_relation %>%
  filter(BoxOffice!="N/A")
tidy_relation$BoxOffice <- tidy_relation$BoxOffice %>%
  str_replace_all(",","") %>%
  str_replace_all("\\$","") %>%
  as.numeric()
tidy_relation %>%
  ggplot(aes(imdbRating,BoxOffice)) + 
  geom_boxplot()+
  theme(axis.text.x = element_text(size = 5,angle = 90))+
  ggtitle("boxplot between rating and boxoffice")
tidy_relation%>%filter(BoxOffice == max(tidy_relation$BoxOffice))
tidy_relation %>% 
  mutate(rank=min_rank(desc(BoxOffice)))%>%
  arrange(rank)%>%
  head()
tidy_relation %>% 
  mutate(rank=min_rank(BoxOffice))%>%
  arrange(rank)%>%
  head()
```

3. NY Times API
(1) the dark knight
In part two OMDb API, the movie “The Dark Knight” talent showing itself because it gets both the second largest box office and third highest rating value, which is rare among the 250 movies. Personally, “The Dark Knight” is also one of my favorite movies. Thus, I decide to do some research on the review of this movie via NY Times API in this part. 

After getting my api-key and specifically searching for key word “The dark knight”, I only get two results from a writer, Manohla Dargis. Among the two results, one is about the third movie of the batman series “The dark knight: rise”. Thus, there is only one movie review for me to analysis.

Then, I get the url from the results of using API and scrap the text of the article using html nodes “p”. Deleting the beginning and the end, I finally get a new data frame with 12 observations, each observation contains a paragraph of the article. Unnesting the paragraph into single word, anti-joinning with the stop words database, and count the number of appearances of each word, I get the data frame of common non-stop words in the article. Visualizing it using “wordcloud” package.
```{r}
#specifically choose film "dark knight"
url4 <- 
  paste0(
    "https://api.nytimes.com/svc/movies/v2/reviews/search.json?query=dark%20knight&api-key=",api.key.Xu.nytimes)
dark_knight<- url4%>% curl() %>% readLines() %>%
  prettify() %>%
  fromJSON()%>%as.data.frame()
dark_knight <- dark_knight %>%
  filter(results.display_title == "The Dark Knight")
dark_knight
dark_knight$results.link$url
#analysis the article
article <- dark_knight$results.link$url %>%
  read_html() %>%
  html_nodes("p") %>% html_text()
article.tbl <- tibble(text=article) %>%
  filter(text !="Advertisement")
article.tbl <-article.tbl[3:14,1]
tidy_article <-article.tbl %>%
  unnest_tokens(word,text)
data("stop_words")
tidy_article %>% 
  anti_join(stop_words) %>%
  count(word, sort = TRUE) %>%  
  filter(n >= 4) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) + 
  geom_bar(stat = "identity") +
  xlab(NULL) + coord_flip() +
  ggtitle("most common non-stop-words in article")
tidy_article %>% 
  anti_join(stop_words) %>%
  count(word, sort = TRUE) %>%  
  filter(n >= 4) %>%
  mutate(word = reorder(word, n)) %>%
  with(wordcloud(word, n, max.words = 100))
```
I find that the most common non-stop word is “batman”. Second common word is “joker”, who contributes a lot and makes this movie incredible. The name of the director also shows up, together with other word which describe the background of the movie. What I did not deal with is words such as “batman’s” “nolan’s”. It should be treated same as “batman” and “Nolan”.

I also tried simply sentiment analysis for the article by inner-joinning get_sentiments with unnested word from each paragraph and calculating the sentiment points of each paragraph. 

```{r}
#simple sentiment analysis of this article
tidy_sentiment <- article.tbl %>%
  mutate(paranum = row_number()) %>%
  unnest_tokens(word,text)
darkknightsentiment <- tidy_sentiment %>%
  inner_join(get_sentiments("bing")) %>%
  count(index = paranum, sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative)
ggplot(darkknightsentiment,aes(index, sentiment)) +
  geom_bar(alpha = 0.8, stat = "identity", show.legend = FALSE) +
  ggtitle("sentiment analysis of dark knight review")
article.tbl[7,1][[1]]
```
From the results I find that apart from the seventh paragraph, the critics is using more negative words when reviewing this movie. The result is consistent with the dark background of the movie. I also look into the only exception: paragraph 7 by calling the text from the original data frame. In seventh paragraph, the review emphasis the room for brightness and romances in the movie and that is why the sentiment analysis shows positive.

(2) Compare with the dark knight rises
My initial idea of using NY Times API is to compare reviews of a movie from different critics. However, later I discover that there is only one review for each movie on NY Times database, so I decide to compare reviews of series movies from one specific critics. Here I choose Manohla Dargis, who also write review of “The Dark Knight Rises”. I repeat the steps in (1) and get common non-stop words and sentiment analysis of the article. 
```{r}
#adding dark knight rises
dark_knight_rise<- url4%>% curl() %>% readLines() %>%
  prettify() %>%
  fromJSON()%>%as.data.frame()
dark_knight_rise<- dark_knight_rise %>%
  filter(results.display_title != "The Dark Knight")
dark_knight_rise$results.link$url
article1 <- dark_knight_rise$results.link$url %>%
  read_html() %>%
  html_nodes("p") %>% html_text()
article.tbl1 <- tibble(text=article1) %>%
  filter(text !="Advertisement")
article.tbl <-article.tbl[3:19,1]

tidy_article1 <-article.tbl1 %>%
  unnest_tokens(word,text)
tidy_article1 %>% 
  anti_join(stop_words) %>%
  count(word, sort = TRUE) %>%  
  filter(n >= 4) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) + 
  geom_bar(stat = "identity") +
  xlab(NULL) + coord_flip() +
  ggtitle("most common non-stop-words in article")
tidy_article1 %>% 
  anti_join(stop_words) %>%
  count(word, sort = TRUE) %>%  
  filter(n >= 4) %>%
  mutate(word = reorder(word, n)) %>%
  with(wordcloud(word, n, max.words = 100))

tidy_sentiment1 <- article.tbl1 %>%
  mutate(paranum = row_number()) %>%
  unnest_tokens(word,text)
darkknightrisesentiment <- tidy_sentiment1 %>%
  inner_join(get_sentiments("bing")) %>%
  count(index = paranum, sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative)
ggplot(darkknightrisesentiment,aes(index, sentiment)) +
  geom_bar(alpha = 0.8, stat = "identity", show.legend = FALSE) +
  ggtitle("sentiment analysis of dark knight rises review")
```
Compare results in (1) and (2), I found that the sentiment of “The Dark Knight Rises” article is a bit more positive than that of “The Dark Knight” article. The common non-stop words of the two articles show some similarity. 
